Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-22 NEUROC/sec3-experiment-design.tex

    \item[Q1] \emph{How do the hyper-parameters affect the training time, the memory usage, and the accuracy of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})
          % TODO: 进一步修改
          Every GNN has a group of hyper-parameters, such as the number of GNN layers and the dimensions of hidden feature vectors.
          %
          The hyper-parameters affect the training time per epoch and the peak memory usage during training.
          %
          To evaluate their effects, we measured how the training time per epoch, the peak memory usage (of the GPU), and the accuracy changed as we increased the values of the hyper-parameters.
          %
          Through the experiments, we verified the validity of the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
          %
          The complexity analysis allowed us to analyze performance bottlenecks theoretically.

>>>>

    \item[Q1] \emph{How do the hyper-parameters affect the training/inference time and memory usage of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})

          Every GNN has a group of hyper-parameters, such as the number of GNN layers and the dimensions of hidden feature vectors.
          %
          The hyper-parameters affect the processing time per epoch and the peak memory usage during training and inference.
          %
          To evaluate their effects, we measured how the training time per epoch, the peak memory usage (of the GPU), and the accuracy changed as we increased the values of the hyper-parameters.
          %
          Through the experiments, we verified the validity of the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
          %
          The complexity analysis allowed us to analyze performance bottlenecks theoretically.
